Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-21 paper.tex
save

Experiments carried out to study the impact of the proposed algorithmic
components and refinements, as described in Section~\ref{methods}, follow a
standard 3-fold cross-validation protocol, using ${\cal S}^\prime$ as
ground-truth dataset. To mimic the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
of claimed signatures with respect to the total set of signatures, as on the
INSPIRE platform, cross-validation folds are constructed by sampling a training
set ${\cal S}_\text{train}^\prime \subseteq {\cal S}^\prime$ of 13\% of claimed
signatures and using the remaining signatures for testing. Accordingly, ${\cal
C}_\text{train}^\prime = \{ c^\prime \cap {\cal S}_\text{train}^\prime |
c^\prime \in {\cal C}^\prime \}$ is used to represent the partial known
clusters on the training fold.

As commonly used in author disambiguation research \citep{levin2012citation},
we evaluate the predicted clusters over training data ${\cal
C}_\text{train}^\prime$, testing data ${\cal C}_\text{test}^\prime$ and the
whole data ${\cal C}^\prime$, using both B3 \glnote{add ref} and pairwise \glnote{add ref} precision, recall
and F-measure, as defined below:
\begin{align}
P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|\widehat{c}(s)|} \\
R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|c(s)|}\\
F_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}{P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) + P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}\\
P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p(\widehat{\cal C})|}\\
R_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p({\cal C})|}\\
F_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{2 P_\text{pairwise}({\cal C}, \widehat{\cal C}) R_\text{pairwise}({\cal C}, \widehat{\cal C})}{P_\text{pairwise}({\cal C}, \widehat{\cal C}) + R_\text{pairwise}({\cal C}, \widehat{\cal C})}
\end{align}
where $c(s)$ (resp. $\widehat{c}(s)$) is the cluster $c \in {\cal C}$ such that
$s \in c$ (resp. the cluster $\widehat{c} \in \widehat{\cal C}$ such that $s
\in \widehat{c}$), and where $p({\cal C}) = \cup_{c \in {\cal C}} \{ (s_1, s_2)
| s_1, s_2 \in c, s_1 \neq s_2 \}$ is the set of all pairs of signatures from
the same clusters in ${\cal C}$. Intuitively, precision evaluates if signatures
are grouped only with signatures from the same true clusters, while recall
measures the extent to which all signatures from the same true clusters are
effectively grouped together. The F-measure is the harmonic mean between these
two quantities. In the analysis below, we rely primarily on B3 measures for discussing
the results, as pairwise measures tend to favor large clusters (because the number of pairs is quadratic with the cluster size),
hence unfairly giving preference to authors with many publications.

% measures (b^3, paired, size of clusters)
% training / valid / test sets

\subsection{Base experiment}

@@

\subsection{Blocking}

@@

\subsection{Learning a linkage function}
% feature engineering
% variable importance analysis
% supervised learning model

\subsection{Semi-supervised clustering}
% compare agglomerative algorithms
% compare threshold strategies
% compare cold start solutions

>>>>

Experiments carried out to study the impact of the proposed algorithmic
components and refinements, as described in Section~\ref{methods}, follow a
standard 3-fold cross-validation protocol, using ${\cal S}^\prime$ as
ground-truth dataset. To replicate the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
of claimed signatures with respect to the total set of signatures, as on the
INSPIRE platform, cross-validation folds are constructed by sampling a training
set ${\cal S}_\text{train}^\prime \subseteq {\cal S}^\prime$ of 13\% of claimed
signatures, and by using the remaining signatures ${\cal S}_\text{test}^\prime = {\cal S}^\prime \setminus {\cal S}_\text{train}^\prime$ for testing. Accordingly, ${\cal
C}_\text{train}^\prime = \{ c^\prime \cap {\cal S}_\text{train}^\prime |
c^\prime \in {\cal C}^\prime \}$ represents the partial known
clusters on the training fold, while ${\cal C}_\text{test}^\prime$ are those
used for testing.

As commonly done in author disambiguation research \citep{levin2012citation},
we evaluate the predicted clusters over training data ${\cal
C}_\text{train}^\prime$, testing data ${\cal C}_\text{test}^\prime$ and the
whole data ${\cal C}^\prime$, using both B3 \glnote{add ref} and pairwise \glnote{add ref} precision, recall
and F-measure, as defined below:
\begin{align}
P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|\widehat{c}(s)|} \\
R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|c(s)|}\\
F_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}{P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) + P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}\\
P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p(\widehat{\cal C})|}\\
R_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p({\cal C})|}\\
F_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{2 P_\text{pairwise}({\cal C}, \widehat{\cal C}) R_\text{pairwise}({\cal C}, \widehat{\cal C})}{P_\text{pairwise}({\cal C}, \widehat{\cal C}) + R_\text{pairwise}({\cal C}, \widehat{\cal C})}
\end{align}
where $c(s)$ (resp. $\widehat{c}(s)$) is the cluster $c \in {\cal C}$ such that
$s \in c$ (resp. the cluster $\widehat{c} \in \widehat{\cal C}$ such that $s
\in \widehat{c}$), and where $p({\cal C}) = \cup_{c \in {\cal C}} \{ (s_1, s_2)
| s_1, s_2 \in c, s_1 \neq s_2 \}$ is the set of all pairs of signatures from
the same clusters in ${\cal C}$. Intuitively, precision evaluates if signatures
are grouped only with signatures from the same true clusters, while recall
measures the extent to which all signatures from the same true clusters are
effectively grouped together. The F-measure is the harmonic mean between these
two quantities. In the analysis below, we rely primarily on B3 measures for discussing
the results, as pairwise measures tend to favor large clusters (because the number of pairs is quadratic with the cluster size),
hence unfairly giving preference to authors with many publications. By contrast,
B3 measures weight clusters linearly with respect to their size.

\subsection{Results and discussion}

\textit{Baseline.}

\glnote{Describe baseline}\\
\glnote{Add an uber table of results}

@@

\textit{Blocking.}

\glnote{Discuss baseline + different blocking strategies}\\
\glnote{Discuss blocking in terms of maximum recall}

@@

\textit{Linkage function.}
% feature engineering
% variable importance analysis
% supervised learning model

\textit{Semi-supervised clustering.}
% compare agglomerative algorithms
% compare threshold strategies
% compare cold start solutions
